\documentclass[12pt]{extarticle}

\title{Theatre Science Assessment Form}
\author{Williamson and Denton}
\date{20 February 2020}

\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\microtypecontext{spacing=nonfrench}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[margin=2cm]{geometry}

% Baskerville font, with text figures.
\usepackage[osf]{Baskervaldx}

% For resizebox (for the title page)
\usepackage{graphicx}

\setlength{\tabcolsep}{1em}

\begin{document}

\thispagestyle{empty}

\begin{center}
  \resizebox{5in}{!}{\textsc{theatre science}}\\
  \vspace{0.3cm}
  \resizebox{5in}{!}{\textsc{assessment form}}\\
  \vspace{0.3cm}
  (Audience)\\
  \vspace{0.5cm}
  \textbf{Please fill out after show and leave the completed form on the bar.}
\end{center}

\begin{enumerate}

  \item Have you performed on stage?

  \begin{tabular}{l|l|l|l|l}
    Never & Rarely & Occasionally & A moderate amount & A great deal
  \end{tabular}

  \item The performers were reading their dialogue from the score and following lines marked on the floor.  Did you find this distracting?

  \begin{tabular}{l|l|l|l|l}
    Never &  Rarely & Sometimes & Often & Always
  \end{tabular}

  \item How did having a copy of the score affect your experience of the show?

  \vspace{0.5cm}
  \rule{6in}{1pt}\\
  \vspace{0.5cm}\\
  \rule{6in}{1pt}

  \item Given what you saw tonight, would you be interested in participating in a future Theatre Science experiment?

    \begin{tabular}{l|l}
    No & Yes
    \end{tabular}

  \item Has this show changed your opinion about the nature of authority of information resources?   If yes, how?

  \vspace{0.5cm}
  \rule{6in}{1pt}\\
  \vspace{0.5cm}\\
  \rule{6in}{1pt}

  \item Do you think the show will make you look differently at what you see in the news and online?

  \vspace{0.5cm}
  \rule{6in}{1pt}\\

  \item Was John Cage an effective example?

  \vspace{0.5cm}
  \rule{6in}{1pt}\\

  \item How familiar were you with John Cage before tonight?

  \begin{tabular}{l|l|l|l|l}
    Not at all & Slightly & Somewhat & Moderately & Very
  \end{tabular}

\end{enumerate}


\end{document}
